\EVOSUITE at the SBST 2022 Tool Competition

### 2022-03-13 papers/sbst22/paper_sbst22.tex
Fix format and authors, finish results

\documentclass[sigconf,review,anonymous]{acmart}

@@

\author{%
%
\IEEEauthorblockN{%
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
%Jose Campos\IEEEauthorrefmark{3},
%and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

%\thispagestyle{empty}

@@

\begin{figure*}
  \centering
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
    \label{fig:results30}
  \end{subfigure}
  \hfill
  \begin{subfigure}{\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
    \label{fig:results120}
  \end{subfigure}

  \caption{Creating subfigures in \LaTeX.}
  \label{fig:figures}
\end{figure*}

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. While the coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively),
the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). 
%
The likely reason for this result is that \EVOSUITE ran out of time more
frequently when given more time. Indeed unlike past instances of the
competition we found no crashes of \EVOSUITE (e.g., exceptions thrown by
\EVOSUITE) at all, but in all cases where no tests were generated the \EVOSUITE
process had been killed by the competition setup, suggesting that \EVOSUITE was
using more time than allocated.

>>>>

%\documentclass[sigconf,review,anonymous]{acmart}
\documentclass[sigconf]{acmart}

@@

\author{Sebastian Schweikl}
\affiliation{%
  \institution{University of Passau}
  \city{Passau}
  \country{Germany}
}
%\email{gordon.fraser@uni-passau.de}

\author{Gordon Fraser}
\affiliation{%
  \institution{University of Passau}
  \city{Passau}
  \country{Germany}
}
%\email{gordon.fraser@uni-passau.de}

\author{Andrea Arcuri}
\affiliation{%
  \institution{Kristiania University College and Oslo Metropolitan University}
  \city{Oslo}
  \country{Norway}
}
%\thispagestyle{empty}

@@

\begin{figure}
  \centering
  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
    \label{fig:results30}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.9\columnwidth}
    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
    \label{fig:results120}
  \end{subfigure}

  \caption{Competition results achieved by \EVOSUITE summarised by projects from which the classes under test.}
  \label{fig:figures}
\end{figure}

With an overall score of \score, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
increased from the \budgetShort to the \budgetLong search budget (mean line
coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).

For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
thrown by \EVOSUITE) at all, but in most cases where no tests were generated
the \EVOSUITE process had been killed by the competition setup, suggesting that
\EVOSUITE was using more time than allocated. In one class of the Seata project
errors occurred during the initialisation of the target class, in which case
\EVOSUITE simply gives up since the JVM does not allow instantiation of such
classes.
